%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
    %---------------------------------------------------------
    \cventry
    {Junior Software Developer}
    {IntellijLabs}
    {Saint Petersburg, Russia}
    {Fall 2018 - Present}
    {
    \begin{cvitems}
        \item{Working on the generation of scientific abstracts using neural networks.}
    \end{cvitems}
    }
    %---------------------------------------------------------
    \cventry
    {Software Engineering Intern} % Job title
    {Google} % Organization
    {Munich, Germany} % Location
    {Summer 2018 - Fall 2018} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on a system that makes running offline jobs safer. Added critical security features to the system.}
        \item {Implemented functionality to pause and later to resume the execution of mutations.}
        \item {Added functionality to configure rate limits, that allows controlling the load the system puts on external backends.}
        \item {Configured database deletion policies, that allows to have strict retention policies and save database memory.}
    \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Android developer} % Job title
    {Yandex} % Organization
    {Saint Petersburg, Russia} % Location
    {Fall 2017 - Summer 2018} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Added support for Android Oreo by rewriting old services.}
        \item {Improved search functionality.}
        \item {Worked on the redesign of the application by implementing custom UI components.}
    \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Software Engineering Intern} % Job title
    {Google} % Organization
    {Seattle, US} % Location
    {Summer 2017 - Fall 2017} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided a full-stack implementation of a tool to support Supply Chain Operations.}
        \item {Implemented functionality to add data to requests for tracking particular steps on the installation of machines at Google data-centers.
        }
    \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Android developer} % Job title
    {Yandex} % Organization
    {Saint Petersburg, Russia} % Location
    {Summer 2016 - Summer 2017} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a framework for parameterized integration tests.}
        \item {Set up SonarQube for pull request analysis.}
        \item {Refactored mail operations to utilize RxJava and Gson.}
        \item {Developed a new settings screen for the Android Mail Client.}
    \end{cvitems}
    }
\end{cventries}
